Group 9 Presentation

### 2021-12-07 presentation.Rmd
Added my LDA and SVM code
Added the code for my LDA and SVM models into the presentation

@@

>>>>

```{r LDA}
LDA_model = lda(HeartDisease~., data=train)

preds = predict(LDA_model, test)

acc = sum(ifelse(preds$class == test$HeartDisease, 1, 0))/nrow(test)

table("Preds"=preds$class, "True"=test$HeartDisease)
```

@@

```{r SVM}
SVM_radial = svm(HeartDisease~., data=train, kernel="radial", gamma=0.25, cost=0.4)

preds = predict(SVM_radial, test, type="class")
acc = sum(ifelse(preds == test$HeartDisease, 1, 0))/nrow(test)

table(test$HeartDisease, preds)
```
